Variable Selection

### 2015-07-01 var_select.rmd
deleted outliers and re-ran a bunch of stuff

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')

@@

Start running cforests
Very slow, start with 100 rows only, using only core variables

```{r, echo=FALSE}
all7b<- read.csv('all7b.csv')[,-1]

core<- all7b %>% select(code.client , Discipline ,  client.count , inv.mlsto , Business ,
        Biz.size , Biz.type , no.users , Year , timespan , Num.disc , Num.days , mean.peeps,
        pc.contracttech , hours.perday , profit.mlsto , balance.mlsto , hrs.mlsto , 
        cost.mlsto , dis.sc.mlsto , inv.mlsto , return.pdol , code.contact ,
        pc.director , pc.midtech , pc.midpro , pc.gradpro , pc.seniortech , pc.seniorpro ,
        pc.pro , code.director , code.ProjEng , ProjEng.Pos , num.inv , mean.inv , num.neginv , 
        client.meaninv , client.neginv , client.numinv , client.totinv)

mini.core2 <- all7b %>% select(code.client , Discipline ,  client.count , inv.mlsto , Business ,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol, code.contact,
        pc.director,
        pc.pro , code.director , ProjEng.Pos ,
        client.meaninv , client.neginv , client.numinv , client.totinv)

mini.core3 <- all7b %>%
        select(Discipline , inv.mlsto , Business, client.count,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol, pc.director,
        pc.pro , code.director , ProjEng.Pos,
        client.meaninv , client.neginv , client.numinv , client.totinv)

Try to make all cforests random selection of 200 rows - this time post 2009

```{r anova_varimp, echo=FALSE}
#use mini.core2- all years
system.time(
        aov.all<- aov(return.pdol~.,
                      data= mini.core3)
        )

* no.users - number of people on the job - <<.1%
* code.director - <<.1%
* timespan - 4%
* Num.disc - 5.6%
* Discipline - 5.65%

worst: Business, ProjEng.Pos, client.numinv,

* code.client pval=1 - this is likely because code.contact and code.client are highly correlated
* inv.mlsto pval= .721 - surprising
* client.numinv pval = 0.923 - surprisingly different

train_ind <- sample(seq_len(2355), size = 1570)

train <- mini.core4[train_ind, ]
test <- mini.core4[-train_ind, ]
oob.err<-double(13)
test.err<-double(13)
for(mtry in 1:13){
        fit<-randomForest(return.pdol ~., data=train, mtry=mtry, ntree=400)
        oob.err[mtry]<-fit$mse[400]
        test.err[mtry]<- mean((predict(fit,test)-test$return.pdol)^2)
        cat(mtry," ")
}

#COMPLETELY FLAT - MAY AS WELL USE MTRY = 5????? NOW VARY NUMBER OF TREES

#again, doesn't matter!! line is dead flat. i'm not having much confidence in the predictiveness of this model. 
```

rand.rank<- multi.forest1(data=mini.core2 %>% select(-code.contact, -code.client), nforest=1:10)

* inv.mlsto
* timespan
* no.users
* Discipline
* pc.pro
* client.totinv
* client.numinv
* pc.director
* code.director
* Num.disc
* Business
* Biz.type

* client.neginv
* client.count
* ProjEng.Pos
* Biz.size
* client.meaninv

@@

* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Secondary
* Job.Type.Primary
* Type
* Project.Value
* no.employees
* client.age
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

@@

```{r NA into code.client, echo=FALSE}

@@

#Project.Value - anything with '0' should be 'NA'
all7c[all7c$Project.Value == 0,]$Project.Value<- NA
#check out what the ratios of inv.mlsto/Project.Value are
temp<- all7c %>% select(Project.Value, inv.mlsto,mlsto) %>% filter(!is.na(Project.Value))
temp<- transform(temp, ratio = round(inv.mlsto/Project.Value*100,2))
temp<- temp %>% filter(ratio< 16)
all7c$Project.Value<- ifelse(all7c$mlsto %in% temp$mlsto, all7c$Project.Value, NA)
write.csv(all7c, 'all7c.csv')

@@

@@

vars<- list('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client'
            'client.age', 'contact.count', 'JD.Second', 'client.age', 'Billing.Type', c('dist','Post.Code'),
            c('code.contact','contact.count'), c('Job.Type.Primary','JD.Primary'))
cfor.plotsave<- function(extra= vars){
        for(i in 1:length(vars)){

@@

                q= ggplot(data=var.imp, aes(x=var, y=imp)) + theme(axis.text.x=element_text(angle=45,hjust=1))
                r=q + geom_bar(stat='identity') + 
                        labs(title = extra[[i]])
                #save plot
                ggsave(plot=r,
                       filename=paste('var',i,'.png',sep=''),
                       path= 'C:/Users/n9232371/Documents/Consultbusiness/barplots/cforests/')

@@

cfor.plotsave(extra=vars)

@@

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')

@@

@@

@@

```{r NA into code.client, echo=FALSE}
#Job.Source - 'twitter' should be NA
all7c[all7c$Job.Source %in% 'Twitter',]$Job.Source<- NA

#Billing.Type - 'Estimate' and 'FeeProposal' and 'NoCharge' should be NA
all7c[all7c$Billing.Type %in% c('Estimate','FeeProposal','NoCharge'),]$Billing.Type<- NA

#code.ProjEng - 'Unknown' should be NA
all7c[all7c$code.ProjEng %in% c('Unknown'),]$code.ProjEng<- NA

#ProjEng.Pos - 'Unknown' should be NA
all7c[all7c$ProjEng.Pos %in% c('Unknown'),]$ProjEng.Pos<- NA

#code.Eng2 - 'Unknown' should be NA
all7c[all7c$code.Eng2 %in% c('Unknown'),]$code.Eng2<- NA

@@

#Project.Value - anything with '0' should be 'NA'
all7c[all7c$Project.Value == 0,]$Project.Value<- NA
#check out what the ratios of inv.mlsto/Project.Value are
temp<- all7c %>% select(Project.Value, inv.mlsto,mlsto) %>% filter(!is.na(Project.Value))
temp<- transform(temp, ratio = round(inv.mlsto/Project.Value*100,2))
temp<- temp %>% filter(ratio< 16)
all7c$Project.Value<- ifelse(all7c$mlsto %in% temp$mlsto, all7c$Project.Value, NA)

#delete outliers : return.pdol>30 GONE
all7c %>% filter(return.pdol>3) %>% select(return.pdol, inv.mlsto, hrs.mlsto, dis.sc.mlsto,mlsto, cost.mlsto) %>% arrange(-return.pdol)
all7c<- all7c %>% filter(!return.pdol>3)

#drop levels in each variable
all.vars<- colnames(all7c)
for (i in 1:length(all.vars)){
        if(all7c[,all.vars[i]] %>% class == 'factor'){
        all7c[,all.vars[i]]<- droplevels(all7c[,all.vars[i]])
        }

write.csv(all7c, 'all7c.csv')

all7c<- read.csv('all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

Start running cforests on core list of variables

core<- all7c %>% select(code.client , Discipline ,  client.count , inv.mlsto , Business ,
        Biz.size , Biz.type , no.users , Year , timespan , Num.disc , Num.days , mean.peeps,
        pc.contracttech , hours.perday , profit.mlsto , balance.mlsto , hrs.mlsto , 
        cost.mlsto , dis.sc.mlsto , inv.mlsto , return.pdol , code.contact ,
        pc.director , pc.midtech , pc.midpro , pc.gradpro , pc.seniortech , pc.seniorpro ,
        pc.pro , code.director , code.ProjEng , ProjEng.Pos , num.inv , mean.inv , num.neginv , 
        client.meaninv , client.neginv , client.numinv , client.totinv)

mini.core2 <- all7c %>% select(code.client , Discipline ,  client.count , inv.mlsto , Business ,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol, code.contact,
        pc.director,
        pc.pro , code.director , ProjEng.Pos , code.ProjEng,
        client.meaninv , client.neginv , client.numinv , client.totinv)

mini.core3 <- all7c %>%
        select(Discipline , inv.mlsto , Business, client.count,
        Biz.size , Biz.type , no.users , timespan, Num.disc, 
        return.pdol, pc.director,
        pc.pro , code.director , 
        client.meaninv , client.neginv , client.numinv , client.totinv)

```{r anova_varimp, echo=FALSE}
#use mini.core2- all years

aov.all<- aov(return.pdol~.,
              data= mini.core3)

* no.users - number of people on the job - << 1%
* timespan - << 1%
* Discipline - <<1%
* inv.mlsto - 8.9%
* Business << 1%
* Biz.type - 2%
* pc.pro - .13%

worst: Biz.size, client.numinv, client.neginv, client.meaninv, client.totinv, pc.director, Num.disc, Biz.size

* Num.disc
* pc.director
* Biz.size
* Biz.type = cforest rated this very low

train_ind <- sample(seq_len(nrow(mini.core3)), size = 1546)

train <- mini.core3[train_ind, ]
test <- mini.core3[-train_ind, ]
oob.err<-double(13)
test.err<-double(13)
for(mtry in 1:13){
        fit<-randomForest(return.pdol ~., data=train, mtry=mtry, ntree=400)
        oob.err[mtry]<-fit$mse[400]
        test.err[mtry]<- mean((predict(fit,test)-test$return.pdol)^2)
        cat(mtry," ")
}

#USE MTRY = 5, NOW VARY NUMBER OF TREES

#use 500 trees
```

rand.rank<- multi.forest1(data=mini.core3, nforest=1:10)

* no.users - number of people on the job - << 1%
* timespan - << 1%
* Discipline - <<1%
* inv.mlsto - 8.9%
* Business << 1%
* Biz.type - 2%
* pc.pro - .13%

* inv.mlsto
* timespan
* no.users
* Discipline
* pc.pro
* client.totinv
* pc.director
* code.director
* Num.disc
* Business
* Biz.type
* Biz.size

* client.neginv
* client.count
* ProjEng.Pos
* client.numinv
* client.meaninv

#### YOU ARE HEREE #####

* ProjEng.Pos
* code.ProjEng
* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Secondary
* Job.Type.Primary
* Type
* Project.Value
* no.employees
* client.age
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

@@

vars<- list('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client',
            'client.age', 'contact.count', 'JD.Second', 'Billing.Type', c('dist','Post.Code'),
            c('code.contact','contact.count'), c('Job.Type.Primary','JD.Primary'))
cfor.plotsave<- function(extra= vars, name= 'vara'){
        for(i in 1:length(vars)){

@@

                q= ggplot(data=var.imp, aes(x=var, y=imp)) + theme(axis.text.x=element_text(angle=45,hjust=1))
                r=q + geom_bar(stat='identity') + 
                        labs(title = extra[[i]])
                #save plot
                ggsave(plot=r,
                       filename=paste(name,i,'.png',sep=''),
                       path= 'C:/Users/n9232371/Documents/Consultbusiness/barplots/cforests/')

@@

cfor.plotsave(extra=vars, name='vara')
cfor.plotsave(extra=vars, name='varb')

all7c %>% select(Job.Detail.Secondary) %>% summary

@@

From the cforests, the extra variables worth keeping are

* code.contact - ranks 2nd after timespan/2nd
* code.client (ranks 4th/4th)
* Project.Value (ranks 3rd/4th)
* no.employees - ranks 7th - before code.director  / 3rd last 
* JD.Second - ranks 6th - before code.director and Num.disc / 5th
* Billing.Type - ranks 3rd last but I can't see how this is not important/last
* Job.Type.Primary - ranks 7th - 6 nice broad categories/4th last

Throwing out:
* Job.Source - ranked last / 3rd last
* Job.Detail.Secondary - too patchy I believe / 3rd last
* Type - nice and broad but didn't seem to work - ranked 4th last / 2nd last
* client.age - 3rd last/last
* contact.count - 4th last/3rd last
* dist - 5th last/last
* Post.Code - 6th last or 7th last 
* contact.count - 3rd last/4th last 
* JD.Primary - 3rd last :(/2nd last

```{r run anova on all, echo=FALSE}
vars.vec<- c('Job.Source', 'Job.Detail.Secondary', 'Type', 'Project.Value', 'no.employees','code.client',
            'client.age', 'contact.count', 'JD.Second', 'Billing.Type', 'dist','Post.Code',
            'code.contact','contact.count', 'Job.Type.Primary','JD.Primary')

aov.loop<- function(extra=vars.vec){
        for (i in 1:length(extra)){
                core.var= all7c[,names(all7c) %in% c('inv.mlsto', 'timespan', 'no.users', 
                                                     'Discipline', 'pc.pro', 
                        'client.totinv', 'client.numinv','pc.director', 'code.director', 'Num.disc', 
                        'Business', 'Biz.type', 'return.pdol', extra[i])]
                core.var = core.var[!is.na(core.var[,extra[i]]),]

                formula = paste("return.pdol ~ inv.mlsto + Discipline + Business+
                        Biz.type + Num.disc +
                        no.users + client.numinv +
                        pc.director + client.totinv + 
                        pc.pro + timespan +
                        code.director +", extra[i], sep="+")

                model= aov(as.formula(formula)              
                           ,data= core.var)

                assign(paste("summ.",extra[i],sep=""), model, envir=.GlobalEnv)

                cat(i," ")
                }
        }

aov.loop(extra=vars.vec)

From Anova, the only new variables that are significant are:

* Project.Value - 17%
* Post.Code - 11.4%
* code.contact - .000013%

Visualise all categorical variables as boxplots vs return.pdol

```{r Tukey Ancova visualisation, echo=FALSE}

all.vars<- colnames(all7c %>% select(-mlsto))

auto.BP<- function(colnames=all.vars, yvar = 'return.pdol', df= all7c, name='box'){

        #make all boxplot dots match colours
        update_geom_defaults("point", list(colour = NULL))

        for (i in 1:length(colnames)){

                #only perform plot if variable is a factor
                #if variable is numeric or an integer, break into 8 bins
                if(df[,colnames[i]] %>% class %in% c('factor')) {

                medians= ddply(all7c,.(all7c[,colnames[i]]), summarise, med=median(return.pdol))

                df[,colnames[i]] <- factor(df[,colnames[i]], 
                                               levels= medians[order(-medians$med),][,1] )

                r= ggplot(df[!is.na(df[,colnames[i]]),],
                       aes_string(x=colnames[i], y=yvar, colour = colnames[i])) + 
                        geom_boxplot(alpha = 0, size = .2, outlier.size = .5)+
                        geom_jitter(alpha= 0.5, size=.2) +
                        labs(title = paste(colnames[i], "vs.", yvar, sep=' '),
                        x= colnames[i],
                        y = yvar) + 
                        theme(legend.position = 'none',
                              text = element_text(size =9.5),
                                axis.text.x= element_text(angle=45, hjust=1))+
                        stat_summary(fun.y = mean, geom= 'point', shape = 1, size = .5)

                #save plot
                ggsave(plot=r,
                       filename=paste(name,i,'.png',sep=''),
                       path= 'C:/Users/n9232371/Documents/Consultbusiness/barplots/boxplots/')

                cat(i," ")  
                }

}
}

auto.BP(colnames=all.vars, yvar = 'return.pdol', df= all7c, name='box')

colnames(all7c)
